Project Proposal

### 2025-02-01 paper/project_proposal.qmd
Corrected Name Update for MYS

---
title: "Project Proposal"
author: 
  - Navya Hooda
  - Mohammed Yusuf Sheikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
---

>>>>

---
title: "Project Proposal"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
---
